Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-23 VMCAI-revised-version/final.tex
appendix minsky

\begin{proposition}\label{indec WSTS with dcs}
{\sc Resilience} and {\sc State-resilience} when $\Safe = \mathopp{\downarrow}~\Safe$ are undecidable for reset-VASS, hence also undecidable for $\post$-effective, $\pred$-basis-effective $\omega^2$-WSTS with strong compatibility.
\end{proposition}

>>>>

We now delve into more details into the undecidability results 
upon which rely
Theorem~\ref{indec WSTS with dcs}
and
Theorem~\ref{srp down up},
namely, that
{\sc Resilience} and {\sc State-resilience} when $\Safe = \mathopp{\downarrow}~\Safe$
are undecidable for Minsky machines
and 
for reset-VASS.

The problems are undecidable for a Minsky machine with at least $3$ counters when
$\Safe$ is downward-closed, since it is possible to guarantee that state $q_f(0,0,0)$ is the only $\Safe$ element potentially reachable from $\Bad$. We then consider a reset-VASS simulating the Minsky machine. We then use Reset-VASS to simulate the Minsky machines~\cite{araki1976PN,dufourd1998reset}, albeit in a weak way. 
% The simulation however is 
Since by a particular choice of $\Safe$ and $\Bad$ we are only interested in the reachability of $q_f(0,0,0)$ in the Minsky machine, 
this weak simulation will be enough to obtain undecidability of both problems.

\begin{proposition}\label{both minsk indec}
{\sc Resilience} and {\sc State-resilience} when $\Safe = \mathopp{\downarrow}~\Safe$ are undecidable for reset-VASS, hence also undecidable for $\post$-effective, $\pred$-basis-effective $\omega^2$-WSTS with strong compatibility.
\end{proposition}
